A free/open-source Kazakh-Tatar machine translation system

### 2013-04-21 paper/paper.tex
concluding remarks

To our knowledge we have presented the first ever MT system between Kazakh and Tatar. It has a near-to-production level
coverage, but relatively small number of rules

@@

We plan to continue development on the pair; the main work will be expanding the dictionaries with new lists of stems, and providing bilingual correspondences. The long-term plan is to integrate the data created with other open-source data for Turkic languages in order to make transfer systems between all the Turkic language pairs.  Related work is currently ongoing with Chuvash--Turkish and Turkish--Kyrgyz.

>>>>

To our knowledge we have presented the first ever MT system between Kazakh and Tatar. It has a near-to-production-level
coverage, but rather a prototype-level number of rules. Though the impact of this relatively low number of rules on the
quality of the translation (compare the WER results for the corpus 1 and corpus 2) looks very promising and suggests
the a high-quality translation between morphologically rich agglutinative languages is possible.

We plan to continue development on the pair; the coverage of the system is already quite high, and although we intend to
increase it to 95% on the corporas we have, the main work will be improving the quality of the translation by adding
more rules, starting with a Constraint Grammar module.
The long-term plan is to integrate the data created with other open-source data for Turkic languages in order to make
transfer systems between all the Turkic language pairs.  Related work is currently ongoing with Chuvash--Turkish and Turkish--Kyrgyz.

@@
